---
title: "Palette maker example"
output:
  rmarkdown::
    github_document
  html_document:
    toc: true
    toc_float: yes
    toc_depth: 2
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)
rm(list=ls())
```


```{r}
source("HLG_Palettemaker_function.R")
```

 -  **package:**     Currently either "brewer" or "viridis"
 -  **pal:**         The sub-palette you want, e.g. "YlGnBu", "magma"
 -  **n:**           How many output colours you want
 -  **reverse :**    Set to true if you want the colors to go the other way
 -  **removeend:**   1 removes the final color, 2 the two final colors etc, default=0
 -  **removestart:** 1 removes the first color, 2 the two first colors etc, default=0
 -  **rgb:**         Set to true to output rgb values, else hex
 
It outputs a list, with the first value a description of the options
and the second a list value with the colors either hex or rgb


<br>

# Examples

### 1. Basic hex


```{r}
package <- "viridis" ; pal <- "viridis"
        n <- 10      ; reverse<-TRUE
removeend <- 0       ; removestart<-2   

hexpal <- palette.function(package,pal,n,rgb=FALSE,reverse,removeend,removestart)
```

<br> 

The first list value is the option you entered

```{r}
print(hexpal[[1]])
```

The second list value are the colours 

```{r}
hexpal[[2]]
```

<br>

```{r}
plot(1:n, 1:n,cex=2,pch=16,col= hexpal[[2]],main=hexpal[[1]])
```


### 2. Make a new variable with your options

```{r}
hexpal <- palette.function("brewer","Blues",n,rgb=FALSE,reverse,removeend,removestart)

# set the colors to be your variable string
eval(parse(text=paste(paste(hexpal[[1]], "<- hexpal[[2]]"))))

plot(1:n, 1:n,cex=2,pch=16,
     col= brewer_Blues_10_remstart2_reversed_hex)
```

<br>

### 3. RGB output to file

Make an rgb output and save output text file to the Output subfolder

```{r}
rgbpal <- palette.function(package,pal,n,rgb=TRUE,reverse,removeend,removestart)

filename <- paste("./Output/",rgbpal[[1]],".txt",sep="")

write.table(rgbpal[[2]],filename ,
            col.names = FALSE,row.names = FALSE,
            quote=FALSE,sep = ",")

```

